Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis

### 2016-04-07 manuscript/manuscript_pve.Rmd
edits from BM
added newphyt cites

\
with respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers. As leaf N reductions were detected with TNC-free leaf mass, it is likely that physical root restriction or decreased supply affected seedling N uptake instead of TNC dilution in leaves in the smallest containers. Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment. Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown. Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to drive changes in root N uptake between free seedlings and seedlings in containers. In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength. Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.

>>>>

\
With respect to nutrient availability, reductions in *A*~n~ were positively correlated with decreases in leaf [N] and leaf N was considerably reduced for seedlings in containers. Since reductions in leaf N were detected with TNC-free leaf mass, it is likely that nutrient uptake was affected in the smallest containers instead of TNC dilution in leaves. It it possible that physical root restriction or decreased supply reduced seedling N uptake in small containers. Although root N was on average higher in free seedlings at the end of the experiment, it was not consistently higher than the smallest container volume treatment. Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown. Soil N also declined evenly across all treatments, providing no clear evidence for decreased supply between free seedlings and seedlings in containers. In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength. Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A*~n~ of seedlings in containers was evident throughout the experiment.
